\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Problem Statement}
\author{Justin Disalvo | Group 64}
\date{11 October 2018}

\begin{document}

\maketitle

\section{Abstract}
Group 64 got together to introduce each other, set up a communication line, and discus how we will move forward. Due to the client not emailing us back, we were left to speculate what the project will be about. We all agree there will be some app, mobile or web, that will tell the user information they are looking for. The group is waiting to hear from the client before going down a path that may be incorrect.

\section{Problem Description}
An existing database of stranded animal locations and dates will be used to create a geographic information system (GIS) with sea surface temperature, wind direction, and current direction. Using this information, science groups will be notified to walk their mile to search for stranded animals along the coasts.

\section{Proposed Solution}
Creating an app that allows users to view information generated from the existing database. This app can be a web application or a mobile application, however, users must be given permission to view certain data that will increase with the users clearance level. This will help prevent anyone who wants to use this information for malicious reasons.\newline 

\noindent Users at level 0, the highest clearance, will be able to view everything. level 1 will be group leaders that can view some extra details about other groups. Level 2 is the crew working for a specific group; they will be able to view any data about their assignment. Level 3 will be everyone else. This app will be open to the public and it will show information on the groups and their progress.

\section{Performance Metrics}
Group 64 has met with each other. However, communication between the client and the group has come to a halt. At the moment, each member can only speculate what the client wants to achieve in this project. So, it is very possible the proposed solution will be nothing, or exactly, like what the client wants.

\end{document}
